### 2012-07-04 inst/examples/Reed.Rmd
Reed lnorm, bev-holt, compare to clark (debug)

``` {r }
f <- function(x,h,p){
	S = x - h
	p[1] * S * (1 - S/p[2]) + S
}
````

With parameters `r` = `r r <- 1` and `K` = `r K <- 100`.

``` {r }
pars <- c(r, K)
````

@@

``` {r  profit}
price <- 1
c0 <- 0.01
c1 <- 0
profit <- profit_harvest(price=price, c0 = c0, c1=c1) 
````

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- .5
````

@@

``` {r noise}
z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
````

@@

``` {r  SDP_Mat}
pdfn <- function(P, s){
  dunif(P, 1 - s, 1 + s)
}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
````

@@

``` {r  }
pdfn2 <- function(P, s){
  dunif(P, 1 - s, 1 + s)
}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, 0.01, pdfn2)
````

>>>>

``` {r }
f <- BevHolt 
````

With parameters `A` = `r A <- 1.5` and `B` = `r B <- 0.005`.

``` {r }
pars <- c(A, B)
````

@@

``` {r  profit}
price <- 1
c0 <- 5
c1 <- 0
profit <- profit_harvest(price=price, c0 = c0, c1=c1) 
````

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- .2
````

@@

``` {r noise}
z_g <- function() rlnorm(1,0, sigma_g)  # 1+(2*runif(1, 0,  1)-1) * sigma_g
````

@@

``` {r  SDP_Mat}
pdfn <- function(P, s){
  # dunif(P, 1 - s, 1 + s)
  dlnorm(P, 0, s)
}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
````

@@

``` {r  }
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, 0.01, pdfn2)
````
